Viscous Transport in Eroding Porous Media

### 2019-05-13 docs/transport/erosion_transport.tex
do the result section of transport paper

>>>>

Besides the channels between two bodies, there is a single channel

For the flat faces at the sites of near contact, since we put the body be close to one another
so we are able to see all the channels between two close bodies have flat faces. 
Besides the channels between bodies, we also observe the flat faces on the bodies 
which are close to the outer boundary. For example, we see the flat faces 
on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.
